Untitled

### 2022-07-06 Manuscript/Lanuza_et_al_2022.Rmd
sup mat edits

The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03). Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization. On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a). However, specialization showed the opposite trend on this axis (figure S9g). On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c). Again, specialization showed the opposite trend to number of visits (figure S9i). [crees que podemos meter una figura de este resultado en main text? Si no esta ahi, no lo va a ver nadie]()

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=28,out.width="90%",fig.align='center',fig.cap="\\textbf{Fig. S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics.", fig.pos= "h"}

#library(brms) #modelling
library(cowplot) #panel of plots
library(ggplot2) #plotting
library(patchwork)

setwd("~/Dropbox/PhD/R/Chapter_2")

#read plot generated in other rmd, bms and stan are giving trouble here... This file is created in Species_Level_Metric_Pcs

plot_metrics_pcs <- readRDS("plot_metrics_pcs.rds")

plot_metrics_pcs

>>>>

The variance of the different plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalized degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, specialization \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03). Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - pollinator dependence axis (PC3) for number of visits and specialization. On PC1, number of visits was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a). However, specialization showed the opposite trend on this axis (figure S9g). On PC3, the number of visits was lower for plants with shorter styles and higher pollinator dependence but higher for plant species with longer styles and lower pollinator dependence (figure S9c). Again, specialization showed the opposite trend to number of visits (figure S9i).

### 2022-07-06 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
sup mat edits

library(reshape2)
library(viridis) #COLOUR GGPLOT
#library(MASS)
library(ggplot2)
library(broman) #crayon colours
#library(tidyverse)
library(patchwork) #panel of plots
library(brms)

@@

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
#Plot nicely PC1
analysis_1 <- readRDS("r_bee_families.rds")
dat_analysis <- readRDS("dat_bee_families.rds")
########################################################################################################################

@@

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
  scale_y_log10()+ggtitle("(d)")
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:bee_family",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")

@@

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0))+ 
  scale_color_manual(name="Functional groups",values=c("orange", 
  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")

>>>>

library(reshape2)
library(viridis) #COLOUR GGPLOT
#library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(tidyverse)
library(patchwork) #panel of plots
library(brms)

@@

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=bee_family, colour=bee_family)) + 
geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction), size = 2.5, alpha=0.4) + geom_line(size=1.5)  + 
ylab("") + 
xlab("") +
theme_ms() + 
theme(legend.position = "none",plot.title = element_text(face="bold")) + 
scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet")) + ggtitle("PC3", subtitle = "(c)") +
scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

#Plot nicely PC1
analysis_1 <- readRDS("r_bee_families.rds")
dat_analysis <- readRDS("dat_bee_families.rds")
########################################################################################################################

@@

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + 
geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + 
geom_line(size=1.5) + 
coord_cartesian(ylim=c(1,100),clip="off")+ 
ylab("Number of visits") + 
xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers") +
theme_ms() + 
theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0)) + scale_color_manual(name="Functional groups",
values = c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet")) +
scale_y_log10() + ggtitle("(d)") +
annotate(geom = "text", x = -1.7, y =0.2 , label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.7, y =0.12 , label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.2 , label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.12 , label = "Large flowers", size = 8) +
xlab("") +
annotate(geom = "text", x = -0.1, y =0.35 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))

#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:bee_family",points=T)

dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + 
geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + 
geom_line(size=1.5) + 
coord_cartesian(ylim=c(1,100),clip="off")+ 
ylab("") + 
xlab("Low poll. depend. High poll. depend.") +
theme_ms() + 
theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0)) + 
scale_color_manual(name="Functional groups",values=c("orange", 
        "black", "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10() +
ggtitle("(e)") +
annotate(geom = "text", x = -1.7, y =0.2 , label = "Low poll. depend.", size = 8) +
annotate(geom = "text", x = -1.65, y =0.12 , label = "Small floral display", size = 8) + 
annotate(geom = "text", x = 1.8, y =0.2 , label = "High poll. depend.", size = 8) + 
annotate(geom = "text", x = 1.85, y =0.12 , label = "Large floral display", size = 8) +
xlab(NULL) +
annotate(geom = "text", x = -0.1, y =0.35 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

@@

dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + 
geom_point(data = dat_analysis, aes(x = -PC3, 
          y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
coord_cartesian(ylim=c(1,100),clip="off") + 
ylab("") +
theme_ms() + 
theme(legend.position = "none",plot.title = 
        element_text(size=rel(2.95),hjust = 0)) + 
scale_color_manual(name="Functional groups",values=c("orange", 
        "black", "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10() + 
ggtitle("(f)") +
annotate(geom = "text", x = -1.6, y =0.2 , label = "Short styles", size = 8) +
annotate(geom = "text", x = -1.25, y =0.12 , label = "High poll. depend.", size = 8) + 
annotate(geom = "text", x = 1.95, y =0.2 , label = "Long styles", size = 8) + 
annotate(geom = "text", x = 2.3, y =0.12 , label = "Low poll. depend.", size = 8) +
xlab(" \n \n  ") +
annotate(geom = "text", x = 0.25, y =0.35 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

### 2022-07-06 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
sup mat edits

d1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis,
      aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4")+  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("PC1")+
  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
 labs(title = "", subtitle =my_y_title)

@@

d2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis,
                                                                          aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC2")+
  theme_ms() + theme(legend.position = "none")  +
  theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold"))+ labs(title = "", subtitle = my_y_title)
#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC3",points=T)
ce_pc1[[1]]$guild <- "bees"

@@

d3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis,
                                                                          aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("PC3")+
  theme_ms() + theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title)

>>>>

dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)

d1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") +  coord_cartesian(ylim=c(1,100),clip="off") +
ylab("Number of visits") +
theme_ms() + 
theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
labs(title = "", subtitle =my_y_title) +
annotate(geom = "text", x = -1.7, y =-32 , label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.72, y =-42 , label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.8, y =-32 , label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.8, y =-42 , label = "Large flowers", size = 8) +
xlab("") +
annotate(geom = "text", x = -0.1, y =-20 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))

@@

dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)

d2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
coord_cartesian(ylim=c(1,100),clip="off") +
ylab("") + 
theme_ms() + 
theme(legend.position = "none")  +
theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
annotate(geom = "text", x = -1.7, y =-32 , label = "Low poll. depend.", size = 8) +
annotate(geom = "text", x = -1.65, y =-42 , label = "Small floral display", size = 8) + 
annotate(geom = "text", x = 1.75, y =-32 , label = "High poll. depend.", size = 8) + 
annotate(geom = "text", x = 1.8, y =-42 , label = "Large floral display", size = 8) +
xlab(NULL) +
annotate(geom = "text", x = -0.1, y =-20 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

#Plot nicely PC3
ce_pc3 <- conditional_effects(analysis_1_just_bees_non_apis, effects = "PC3",points=T)
ce_pc1[[1]]$guild <- "bees"

@@

dat_analysis <- dat_analysis %>% dplyr::filter(Interaction<100)

d3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
coord_cartesian(ylim=c(1,100),clip="off") +
ylab("") + 
theme_ms() + 
theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
annotate(geom = "text", x = -1.6, y =-32 , label = "Short styles", size = 8) +
annotate(geom = "text", x = -1.2, y =-42 , label = "High poll. depend.", size = 8) + 
annotate(geom = "text", x = 1.95, y =-32 , label = "Long styles", size = 8) + 
annotate(geom = "text", x = 2.3, y =-42 , label = "Low poll. depend.", size = 8) +
xlab(" \n \n  ") +
annotate(geom = "text", x = 0.25, y =-20 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

### 2022-07-06 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
sup mat edits

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1") + ggtitle(NULL, subtitle = "(g)") +  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")

@@

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC2") + ggtitle(NULL, subtitle = "(h)") + xlab("Low poll. depend.   High poll. depend.")

@@

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
 size = 3.5, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC3") + ggtitle(NULL, subtitle = "(i)")+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")

>>>>

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + 
geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
           size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
            clip="off") + 
           theme_ms() +
geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, 
            alpha=0.1,fill="black") + ylab("Specialization (d')") + 
xlab("PC1") + 
ggtitle(NULL, subtitle = "(g)") +  
annotate(geom = "text", x = -1.6, y =-0.3 , 
               label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.7, y =-0.41 ,
               label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.75, y =-0.3 , 
               label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.75, y =-0.41 ,
               label = "Large flowers", size = 8) +
annotate(geom = "text", x = 0.10, y =-0.19 , 
    label = "Flower number - Flower size axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2)) +
xlab(" \n \n  ")

@@

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y =
(estimate__))) + 
geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
           size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
                clip="off") +
theme_ms() +
geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + 
ylab(NULL) + 
xlab("PC2") + 
ggtitle(NULL, subtitle = "(h)") + 
xlab(NULL) +
annotate(geom = "text", x = -1.57, y =-0.3 , 
               label = "Low poll. depend.", size = 8) +
annotate(geom = "text", x = -1.5, y =-0.41 ,
               label = "Small floral display", size = 8) + 
annotate(geom = "text", x = 1.75, y =-0.3 , 
               label = "High poll. depend.", size = 8) + 
annotate(geom = "text", x = 1.8, y =-0.41 ,
               label = "Large floral display", size = 8) +
annotate(geom = "text", x = 0.10, y =-0.19 , 
    label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

@@

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y =             (estimate__))) + 
geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
           size = 3.5, alpha=0.65, colour="darkorange3")  +
theme_ms() + 
geom_line(colour="black",size=1.5) +
geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2,    
            alpha=0.1,fill="black") +
ylab(NULL) + 
xlab("PC3") + 
coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
                clip="off") +
ggtitle(NULL, subtitle = "(i)") + 
annotate(geom = "text", x = -1.57, y =-0.3 , 
         label = "Short styles", size = 8) +
annotate(geom = "text", x = -1.25, y =-0.41 ,
         label = "High poll. depend.", size = 8) + 
annotate(geom = "text", x = 2.05, y =-0.3 , 
         label = "Long styles", size = 8) + 
annotate(geom = "text", x = 2.4, y =-0.41 ,
         label = "Low poll. depend.", size = 8) +
annotate(geom = "text", x = 0.25, y =-0.19 , 
         label = "Style length - Pollinator dependence axis", 
         size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2)) +
xlab(NULL)
